Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-18 doc/JFLA2022/paper.tex
be precise about coq-community founders

\subsection{Vision}
The \Hydras project, part of \community on GitHub~\cite{CoqCommunity}, aims to be an experimental platform for the collaborative development of documented libraries of formal proofs. \community is a community organization that we founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting \coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting \coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries~\cite{CantorContrib,AdditionsContrib} (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel}, and a bridge to the \gaia library by José Grimm~\cite{Gaia,grimm:hal-00911710}.
%
By following this approach of commenting interesting \coq packages, we provide new documentation content that contributes to the diversity of the thriving \coq ecosystem.

>>>>

\subsection{Vision}
The \Hydras project, part of \community on GitHub~\cite{CoqCommunity}, aims to be an experimental platform for the collaborative development of documented libraries of formal proofs. \community is a community organization that the first and last authors founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting \coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting \coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries~\cite{CantorContrib,AdditionsContrib} (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel}, and a bridge to the \gaia library by José Grimm~\cite{Gaia,grimm:hal-00911710}.
%
By following this approach of commenting interesting \coq packages, we provide new documentation content that contributes to the diversity of the thriving \coq ecosystem.
